Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-04-19 Moltres.tex
adds abstract

>>>>

\begin{abstract}
        This work introduces Moltres, a new physics application for multiphysics modeling of 
        fluid-fuelled molten salt reactors. The neutronics model, thermal 
        hydraulics model, and their coupling in the MOOSE framework are 
        described. Validation against other coupled models as well as experimental 
        results from the Molten Salt Reactor Experiment are demonstrated.
\end{abstract}
